\section{Publications}

\begin{itemize}[leftmargin=0.15in, label={}] % \resumeSubHeadingListStart
    \item My academic publications are also listed on \href{https://scholar.google.com.br/citations?user=Kj6Gzs4AAAAJ&hl=pt-BR&oi=sra}{Google scholar}.
    \item \textbf{Theses}
    \begin{itemize}%[label={-}]
        \item Doctorate's thesis (in progress), ``Modeling, detection and characterization of the equatorial ionospheric scintillation signal in GNSS receivers''. Adivised by Prof. Dr. Felix Dieter Antreich and Prof. Dr. André Lima Ferrer de Almeida.
        \item Master's thesis, \href{http://repositorio.ufc.br/bitstream/riufc/60259/1/2021_dis_rvpacelli.pdf}{``Coherent and all-digital AFSK modem for TT\&C module of CubeSat systems''} (in Portuguese). Advised by Prof. Dr. João Cesar Moura Mota and Prof. Dr. Antônio Macilio Pereira de Lucena.
        \item Bachelor's thesis, ``Design of a portable charger converter with USB Type-C interface.'' (in Portuguese). Advised by Prof. Dr. Bruno Ricardo de Almeida. Universidade de Fortaleza (UNIFOR).
    \end{itemize}
    \item \textbf{Journal Articles}
    \begin{enumerate}[label=\textbf{J\arabic*.}, align=left, leftmargin=1.5cm]
        \item \textit{Pacelli, R. V.}; \textit{Lucena, A. M. P.} . \href{https://www.brazilianjournals.com/index.php/BRJD/article/view/8538/7345}{Fully digital GMSK modem with noncoherent demodulation} (in Portuguese). Brazilian Journal of Development, v. 6, p. 17988-17996, 2020.
        \item \textit{Pacelli, R. V.}; \textit{Lucena, A. M. P.} ; \textit{Figueiredo, S. S.} . \href{https://www.brazilianjournals.com/index.php/BRJD/article/view/7944/6883}{Carrier synchronization technique for OFDM communication systems} (in Portuguese). Brazilian Journal of Development, v. 6, p. 14297-14305, 2020.
        \item \textit{Figueiredo, S. S.} ; \textit{Lucena, A. M. P.} ; \textit{Pacelli, R. V.} . \href{https://www.brazilianjournals.com/index.php/BRJD/article/view/7946/6889}{Carrier selection technique for OFDM system in time-dispersive channels} (in Portuguese). Brazilian Journal of Development, v. 6, p. 14318-14324, 2020.
        \item \textit{Pacelli, R. V.}; \textit{Lucena, A. M. P.} . \href{https://periodicos.unifor.br/tec/article/view/7506/5991}{OFDM system with frequency and phase estimators for carrier synchronization} (in Portuguese). Revista Tecnologia, v. p. 40, 1-16, 2019.
    \end{enumerate}
    \item \textbf{Conference Proceedings}
    \begin{enumerate}[label=\textbf{C\arabic*.}, align=left, leftmargin=1.5cm]
        \item \textit{Moreira, N. A.} ; \textit{Pacelli, R. V.} ; \textit{Silva, Y. C. B.} ; \textit{Maciel, T. F.} ;\textit{Simoes, I.} ; \textit{Mota, J. C. M.} ; \textit{Hamida, C.} ; \textit{Prado, R. Z.} ; \textit{Caillault, E.} ; \textit{Kacou, M.} ; \textit{Gosset, M.}. \href{https://www.sba.org.br/cba2022/wp-content/uploads/artigos_cba2022/paper_2351.pdf}{Convolutional Long-Short-Term Memory Networks (ConvLSTM) for Weather Prediction using Radar and Satellite Images}. In: XXIV Congresso Brasileiro De Automática - CBA 2022, 2022.
        \item \textit{Pacelli, R. V.} ; \textit{Lucena, A. M. P.} ; \textit{Mota J. C. M.}. \href{http://www.sbrt.org.br/sbrt2020/papers/1570654898.pdf}{All-digital AFSK modem with Viterbi detection for TT\&C CubeSat transceiver}. In: XXXVIII Simpósio Brasileiro de Telecomunicações e Processamento de Sinais - SBrT 2020, 2020.
        \item \textit{Mourao, J. A.} ; \textit{Lucena, A. M. P.} ; \textit{Araujo, D. C.} ; \textit{Pacelli, R. V.} . \href{https://uol.unifor.br/oul/conteudosite/?cdConteudo=6946081}{A technique for frequency synchronization in OFDM modulation} (in Portuguese). In: Encontros Científicos 2016, Fortaleza. XXII - Encontro de iniciação à pesquisa, 2016. v. XXII.
    \end{enumerate}
    \item \textbf{Book Chapter}
    \begin{enumerate}[label=\textbf{BC\arabic*.}, align=left, leftmargin=1.5cm]
        \item \textit{Pacelli, R. V.}; \textit{Lucena, A. M. P.} ; \textit{Araujo, D. C.} ; \textit{Mourao, J. A.}. \href{https://www.finersistemas.com/atenaeditora/index.php/admin/api/ebookPDF/3771}{Symbol time synchronization in OFDM systems} (in Portuguese), chapter in Sales F. O. (Org). Ciências Exatas e da Terra: Exploração e Qualificação de Diferentes Tecnologias 4. Atena Editora, 2021, v. 4, p. 200-207.
        \item \textit{Pacelli, R. V.} ; \textit{Lucena, A. M. P.}. \href{https://www.brazilianjournals.com.br/assets/ebooks/2c9747ceb79e967166c7d80a9ff8e1da.pdf}{GMSK modem with noncoherent demodulation and all-digital implementation} (in Portuguese), chapter in Catapan, E. A (Org). Os impactos de estudos voltados para as ciências exatas. Brazilian Journals Editora, 2020, v. 01, 1st ed, p. 21-30.
    \end{enumerate}
\end{itemize}